---
title: "Area Overview"
author: "Eli Pousson"
date: "11/15/2020"
output: html_document
params:
  area_name:
    label: "Area name/list:"
    value: "Baltimore Highlands"
    input: text
  area_label:
    label: "Area label:"
    value: "Baltimore Highlands"
    input: text
  area_type:
    label: "Area type:"
    value: neighborhood
    input: select
    choices: [neighborhood, council_district, police_district, csa, block_group, tract]
---

```{r setup, include=FALSE, warning=FALSE}
knitr::opts_chunk$set(echo = TRUE)

library(mapbaltimore)

map_theme <- ggplot2::theme_minimal() +
  ggplot2::theme(
    panel.grid.major = ggplot2::element_line(color = "transparent"),
    axis.title = ggplot2::element_text(color = "transparent"),
    axis.text = ggplot2::element_text(color = "transparent")
  )

# Load saved ACS data created by 01_import_data.R script
overview_acs <- readRDS("data/overview_acs.rda")
```

This parameterized R Markdown document explores how to use the mapbaltimore package in combination with ggplot and the tidycensus package to create a basic profile of a neighborhood or group of neighborhoods in Baltimore, Maryland. The functions defined below (from the utils.R script) may be added to the mapbaltimore package if they prove useful.

```{r, code=readLines("R/utils.R")}
```

```{r select_area}
# Testing with multiple neighborhoods
# selected_area_name <- c("Central Forest Park", "Concerned Citizens Of Forest Park", "Forest Park", "Forest Park Golf Course", "West Forest Park")
# selected_area_label <- "Forest Park Planning Area"

selected_area_name <- params$area_name
selected_area_type <- params$area_type
selected_area_label <- params$area_label

# Get area
selected_area <- get_area(area_type = selected_area_type,
                          area_name = selected_area_name)

# Get buffered area
buffered_selected_area <- get_buffered_area(selected_area)
buffered_selected_area_bbox <- sf::st_bbox(buffered_selected_area)
```

```{r satellite, warning=FALSE}
# Map satellite view of the area
area_satellite_map <- ggplot2::ggplot() +
  snapbox::layer_mapbox(
    area = buffered_selected_area_bbox,
    map_style = stylebox::mapbox_satellite_streets()
  ) +
  ggplot2::geom_sf(
    data = sf::st_difference(
      sf::st_as_sfc(buffered_selected_area_bbox),
      sf::st_union(selected_area)), # The st_union call is only required if multiple areas are provided
    fill = "white",
    color = "white",
    alpha = 0.4
    ) +
  ggplot2::geom_sf(
    data = selected_area,
    fill = NA,
    color = "black",
    linetype = 5
  ) +
  map_theme

# Get nearby areas
nearby_areas <- get_nearby_areas(area = selected_area,
                                 area_type = selected_area_type)

# Map nearby areas
nearby_areas_map <- ggplot2::ggplot() +
  ggplot2::geom_sf(
    data = nearby_areas,
    ggplot2::aes(fill = name),
    color = "white",
    alpha = 0.4
    ) +
  ggplot2::scale_fill_viridis_d() +
  ggplot2::guides(fill = "none") +
  ggplot2::geom_sf_label(
    data = nearby_areas,
    ggplot2::aes(label = name),
    fill = "white",
    color = "black"
    ) +
  ggplot2::geom_sf(
    data = selected_area,
    fill = NA,
    color = "black",
    linetype = 5
  ) +
  map_theme

area_satellite_map
```

```{r area_in_city}

selected_area_union <- sf::st_sf(geometry = sf::st_union(selected_area))

selected_area_union$name <- selected_area_label
             
area_in_city_map <- map_area_in_city(area = selected_area_union) +
  ggplot2::theme(
  title = ggplot2::element_text(family = "Roboto Condensed", size = 10)
  )

area_in_city_map

```

## Census data analysis

```{r tracts, warning=FALSE}
# Get area census tracts
selected_area_tracts <- get_area_tracts(selected_area)

# Get buffered area for tracts
buffered_selected_area_tracts <- get_buffered_area(selected_area_tracts)
buffered_selected_area_tracts_bbox <- sf::st_bbox(selected_area_tracts)

tract_map <- ggplot2::ggplot() +
  snapbox::layer_mapbox(
    area = buffered_selected_area_tracts_bbox,
    map_style = stylebox::mapbox_light()
  ) +
  ggplot2::geom_sf(
    data = selected_area_tracts,
    ggplot2::aes(fill = namelsad),
    color = "white",
    alpha = 0.4
    ) +
  ggplot2::scale_fill_viridis_d() +
  ggplot2::geom_sf(
    data = selected_area,
    fill = NA,
    color = "black",
    linetype = 5
  ) +
  ggplot2::geom_sf_label(
    data = selected_area_tracts,
    ggplot2::aes(label = namelsad)
  ) +
  map_theme +
  ggplot2::labs(
    fill = "Tract name"
  )

tract_map
```

```{r demographics}

acs_plot_theme <- ggplot2::theme(
  axis.title = ggplot2::element_text(family = "Roboto Condensed", size = 12),
  axis.text = ggplot2::element_text(family = "Roboto Condensed", size = 10)
)

# Plot Race
plot_acs_table(selected_area_tracts, table_id = "B02001", level = "primary") + acs_plot_theme
# NOTE: Not relevant for all areas

# Plot Nativity and Citizenship Status in U.S. in selected area tracts
plot_acs_table(selected_area_tracts, table_id = "B05001", level = "primary") + acs_plot_theme

# Plot Hispanic or Latino By Race
# plot_acs_table(selected_area_tracts, table_id = "B03002", level = "secondary")

# Plot Hispanic or Latino Origin
plot_acs_table(selected_area_tracts, table_id = "B03003", level = "primary") + acs_plot_theme

```

```{r housing}
# Plot Occupancy Status
plot_acs_table(selected_area_tracts, table_id = "B25002", level = "primary") + acs_plot_theme

# Plot Tenure
plot_acs_table(selected_area_tracts, table_id = "B25003", level = "primary") + acs_plot_theme

# Plot Rooms
plot_acs_table(selected_area_tracts, table_id = "B25017", level = "primary") + acs_plot_theme

# Plot Number of Units
plot_acs_table(selected_area_tracts, table_id = "B25024", level = "primary") + acs_plot_theme

# Plot Year Built
plot_acs_table(selected_area_tracts, table_id = "B25034", level = "primary") + acs_plot_theme

# Plot home value
plot_acs_table(selected_area_tracts, table_id = "B25075", level = "primary") + acs_plot_theme
```

